Cross-culture differences in tourists faced with Japanese hospitality: A text mining and rank-biased overlap measure study of satisfaction and dissatisfaction factors in Chinese and Western cultures

### 2020-09-27 2_revisions/V1_ITT submit version/itt-emotion_V1.tex
First data commit: V2-1, before second review

\author{REDACTED
}

\authorrunning{REDACTED}

\institute{REDACTED
}

@@

REDACTED

>>>>

\author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
        Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
        Hirofumi Nonaka                                                 \protect\affmark[1] \and
        Toru Hiraoka                                                    \protect\affmark[2]
}

\authorrunning{E. Alemán Carreón et al.}

\institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
            % Nagaoka University of Technology, Nagaoka, Japan \\
            \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
            \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
            % Corresponding Author %  \\
            % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
        \and
            \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
            % Nagaoka University of Technology, Nagaoka, Japan \\
            \hspace*{1em} \email{mendoza.espana@gmail.com}
        \and
            \hspace*{1em} Hirofumi Nonaka \at
            % Nagaoka University of Technology, Nagaoka, Japan \\
            \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
        \and
            \hspace*{1em} Toru Hiraoka \at
            % University of Nagasaki, Nagasaki, Japan \\
            \hspace*{1em} \email{hiraoka@sun.ac.jp}
        \and
            \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
        \and
            \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
}

% Corresponding author%: \\
% % Elisa Claire Alemán Carreón \\
% % Mailing Address: P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan \\
% % Cell Phone: 080-9869-4756 \\
% % ORCID: 0000-0002-6437-0866

@@

During our research, we received the commentary and discussion necessary to understand certain cultural aspects that could influence the interpretation of the data by our dear colleagues, whom we would like to show gratitude to, Mr. Liangyuan Zhou, Ms. Min Fan and Ms. Eerdengqiqige. We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.

\medskip

Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).

\medskip

Conflict of interest: none

### 2020-09-27 2_revisions/V3_ITT_second revision/itt-emotion_V2-1.tex
First data commit: V2-1, before second review

\author{REDACTED
}

\authorrunning{REDACTED}

\institute{REDACTED
}

@@

REDACTED

>>>>

\author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
        Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
        Hirofumi Nonaka                                                 \protect\affmark[1] \and
        Toru Hiraoka                                                    \protect\affmark[2]
}

\authorrunning{E. Alemán Carreón et al.}

\institute{\Letter \hspace*{0.16em} Elisa Claire Alem\'an Carre\'on  \at
            % Nagaoka University of Technology, Nagaoka, Japan \\
            \hspace*{1em} \email{elisa.claire.aleman.carreon@gmail.com} \\
            \hspace*{1em} ORCID: 0000-0002-6437-0866 %\\
            % Corresponding Author %  \\
            % \emph{Present address:P.C. 940-2033, Ribbon Nagaoka B104, 1128-3 Kaminozoki-machi, Nagaoka, Niigata, Japan}
        \and
            \hspace*{1em} Hugo Alberto Mendoza Espa\~na \at
            % Nagaoka University of Technology, Nagaoka, Japan \\
            \hspace*{1em} \email{mendoza.espana@gmail.com}
        \and
            \hspace*{1em} Hirofumi Nonaka \at
            % Nagaoka University of Technology, Nagaoka, Japan \\
            \hspace*{1em} \email{nonaka@kjs.nagaokaut.ac.jp}
        \and
            \hspace*{1em} Toru Hiraoka \at
            % University of Nagasaki, Nagasaki, Japan \\
            \hspace*{1em} \email{hiraoka@sun.ac.jp}
        \and
            \at \affaddr{\affmark[1] \hspace*{0.15em} Nagaoka University of Technology, Nagaoka, Japan}
        \and
            \at \affaddr{\affmark[2] \hspace*{0.15em} University of Nagasaki, Nagasaki, Japan}
}

@@

During our research, we received the commentary and discussion by our dear colleagues necessary to understand particular cultural aspects that could influence the interpretation of the data. We would like to show gratitude to Mr. Liangyuan Zhou, Ms. Min Fan, and Ms. Eerdengqiqige for this.

We would also like to show gratitude to Ms. Aleksandra Jajus, from whom we also received notes on the editing and commentary on the content of our manuscript.

\medskip

Funding: This work was supported by the Japan Construction Information Center Foundation (JACIC).

\medskip

Conflict of interest: none
